### 2021-05-20 sections/queueing_model/subsections/performance_measures/waiting_time/main.tex
Apply suggestions to waiting time section from code review
Co-authored-by: Vince Knight <vincent.knight@gmail.com>

Consequently, the overall waiting time can be estimated by a linear combination 
of \(W_1\) and \(W_2\). 
Thus, the overall waiting time can calculated by the following equation where 
\(c_1\) and \(c_2\) are the coefficients of the terms:

@@

The two coefficients represent the proportion of individuals of each type that 
did not get lost and traversed through the model.
Thus, one should account for the probability that an individual is lost to the 
system. 
This probability can be easily calculated by using the two sets of accepting 
states \(S_A^{(2)}\) and \(S_A^{(1)}\) defined in equations 
(\ref{eq:accepting_states_type_1}) and (\ref{eq:accepting_states_type_2}). 
Using these equations the probability, for either individual type, that an 
individual is not lost in the system is given by:

>>>>

Consequently, the overall waiting time can be estimated by a linear combination 
of \(W_1\) and \(W_2\). 
Thus, the overall waiting time can be calculated by the following equation where 
\(c_1\) and \(c_2\) are the coefficients of the terms:

@@

The two coefficients represent the proportion of individuals of each type that 
are not lost to the system.
Thus, one should account for the probability that an individual is lost to the 
system. 
This probability can be easily calculated by using the two sets of accepting 
states \(S_A^{(2)}\) and \(S_A^{(1)}\) defined in equations 
(\ref{eq:accepting_states_type_1}) and (\ref{eq:accepting_states_type_2}). 
Using these equations the probability, for either individual type, that an 
individual is not lost in the system is given by:
